Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-06-23 WholePlotTrajectories.tex
Update WholePlotTrajectories.tex

The experiment is a network of twelve 6.25ha plots that underwent a
gradient of three logging, thinning and fuelwood cutting treatments
(Table \ref{tab:Tab1}) attributed according to a randomized plot design
with three replicate blocks of four plots. The disturbance corresponds
to averages of 10 trees removed per hectare with a diameter at 1.3 m
height (DBH) above 50 cm for treatment 1 (T1), 32 trees/ha above 40 cm
DBH for treatment 2 (T2) and 40 trees/ha above 40 cm DBH for treatment 3
(T3). Treatments T2 and T3 besides included the thinning of trees by
poison girdling \citep{Schmitt1990, Blanc2009}. The disturbance
intensity was measured as the percentage of aboveground biomass (\%AGB)
lost between the first inventory in 1984 and five years after
disturbance (ref to be found) measured with the BIOMASS R package
\citep{Biomass2018}.

>>>>

The experiment is a network of twelve 6.25ha plots that underwent a
gradient of three logging, thinning and fuelwood cutting treatments
(Table \ref{tab:Tab1}) attributed according to a randomized plot design
with three replicate blocks of four plots. The disturbance corresponds
to averages of 10 trees removed per hectare with a diameter at 1.3 m
height (DBH) above 50 cm for treatment 1 (T1), 32 trees/ha above 40 cm
DBH for treatment 2 (T2) and 40 trees/ha above 40 cm DBH for treatment 3
(T3). Treatments T2 and T3 besides included the thinning of trees by
poison girdling \citep{Schmitt1990, Blanc2009}. The disturbance
intensity was measured as the percentage of aboveground biomass (\%AGB)
lost between the first inventory in 1984 and five years after
disturbance \citep{Piponiot2016} measured with the BIOMASS R package
\citep{Biomass2018}.
